Towards typed repositories of proofs

### 2010-06-18 papers/MIPS2010/abstract.tex
* Work est indenombrable.
git-svn-id: http://gasp.dev.regis-gianas.com/svn/trunk@124 403e655e-980a-47bd-8c60-1ee5348bb6b7
...
git-svn-id: http://gasp.dev.regis-gianas.com/svn/trunk@125 403e655e-980a-47bd-8c60-1ee5348bb6b7

The kernel of our system is a type-checker algorithm for a typed
meta-language. In this language, we will declare both the syntax of
the object (proof-)language and its typing rules, and define pieces of
syntax (our proofs) and their derivations. Describing transformations
among syntactic objects is done by sharing common subterms or
subderivations.

Representing syntax and logics is nicely done in a \emph{logical
  framework} like LF: both the syntactic elements and the typing
derivations can sit in the same tree structure, and both can be
rechecked at the same time, thanks to dependent types. For the purpose
of incremental type checking though, our needs are a little bit
different: first, we need to record, that is to name all intermediate
values of our developments, so as to be able to address and reuse them
multiple times. Secondly, we need to make sure that those intermediate
values (sub-terms) are not recorded twice, so as to not type-check
them twice: we are looking to represent syntactic and typing objects
as a DAG rather than a tree. Moreover, we enforce by typing a property
of \emph{maximal sharing}: every different subterm can be constructed
exactly once. Our system will have these properties w.r.t. LF:
\begin{itemize}
\item In this first iteration of the project, we do not need
  computations to take place within our DAGs. Our syntax will then be
  restricted to product types and applications;
\item Every term should be a flat application of variables, so that we
  don't introduce compound terms without naming them and recording
  their types;
\item Finally we need a way to record intermediate definitions: we
  introduce a new kind of binder, the equality binder. We maintain the
  invariant that not two same definition can sit in the context while
  typing, thus guaranteeing \emph{maximal sharing} among terms and
  derivations.
\end{itemize}

@@

\paragraph{Related works}
\label{rw}

>>>>

The kernel of our system is a type-checker algorithm for a typed
meta-language. In this language, we will declare both the syntax of
the object (proof-)language and its typing rules, and define pieces of
syntax (our proofs, potentially with omitted informations) and their
derivations (fully explicit application of typing rules). Describing
transformations among syntax objects is done by sharing common
subterms or subderivations.

Representing syntax and logics is nicely done in a \emph{logical
  framework} like LF: both the syntactic elements and the typing
derivations can sit in the same tree structure, and both can be
rechecked at the same time, thanks to dependent types. For the purpose
of incremental type checking though, our needs are a little bit
different: first, we need to record, that is to name all intermediate
values of our developments, so as to be able to address and reuse them
multiple times. Secondly, we need to make sure that those intermediate
values (sub-terms) are not recorded twice, so as to not type-check
them twice: we are looking to represent syntactic and typing objects
as a directed acyclic graph (DAG) rather than a tree. Moreover, we
enforce by typing a property of \emph{maximal sharing}: every
different subterm can be constructed exactly once. Our system will
have these properties w.r.t. LF:
\begin{itemize}
\item In this first iteration of the project, we do not need
  computations to take place within our DAGs. Our syntax will then be
  restricted to product types $(x:t)\cdot t$ and applications;
\item Every term should be a flat application of variables $a ::= \vec x$, so
  that we don't introduce compound terms without naming them and
  recording their types;
\item Finally we need a way to record intermediate definitions: we
  introduce a new kind of binder, the equality binder $(x=a)\cdot
  t$. We maintain the invariant that no two syntactically equal
  definition can sit in the context while typing, thus guaranteeing
  \emph{maximal sharing} among terms and derivations.
\end{itemize}

@@

\paragraph{Related work}
\label{rw}
